Postural developments modulate children's visual access to social information

### 2018-01-31 writeup-cogsci/cogsci2018_faceOnly_alessandro.Rmd
fixed bib and special characters

keywords: "social cognition; face-perception; infancy; locomotion; head-cameras; deep learning"
output: cogsci2016::cogsci_paper
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)
```

```{r, libraries}
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(xtable)
library(lubridate)
library(langcog)
library(ggplot2)
library(ggthemes)
library(egg) # plot arranging
library(lme4)
library(gridExtra)
library(feather)
library(assertthat)
```
# Introduction

From early infancy, children are deeply engaged in learning from others [@csibra2009natural; @meltzoff2007like]. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and young infants follow overt gaze shifts [@gredeback2010development]. Further, when infants attend to video stimuli, they tend to look mostly at faces at the expense of other visual information -- though older infants start to look towards people's hands and the actions they are performing [@frank2012measuring; @frank2014visual].

@@

Recent technological developments allow for testing of this hypothesis by documenting the experiences of infants and children from their own perspective. By using head-mounted cameras, researchers have begun to record the visual experiences of infants and children -- which even for walking children are extremely different from the adult perspective (and not easily predicted by our own adult intuitions) [@clerkin2017;@franchak2011;@yoshida2008]. Children’s views tend to be more restricted and dominated by objects and hands  [@yoshida2008], and computational and empirical work suggest that this restricted viewpoint may be more effective for learning objects and their labels than the comparable adult perspective [@bambach2017;@yurovsky2012]. This perspective changes over the first two years of life, as views transition from primarily containing close up views of faces to capturing views of hands paired with the objects they are acting on [@fausey2016]. These changes may be driven by – or independent from – the concurrent motoric changes described above.

@@

# Function to evaluate detectors
evaluate <- function(a, b) {
  if (a == TRUE) {
    if (a == b) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (a == b) return("TN") # was not face/wrist, detected face/wrist
    else return("FP") # was not face/wrist, said face/wrist
  }
}

## EVALUATE FACE DETECTORS
performanceFaces <- ground_truth_faces  %>%
  mutate(frame=as.numeric(frame), subid=video) %>%
  left_join(dlong)   %>%
  filter(detectorType!="OpenPose-Wrists") %>%
  mutate(detector_is_face = detection, is_face = as.logical(is_face)) %>%
  rowwise() %>%
  mutate(result = evaluate(is_face, detector_is_face))

@@

\begin{table}[ht]
\centering
\begin{tabular}{rllrrr}
\hline
Algorithm & Sample\ Type & P & R & F \\ 
\hline
MTCNN-Faces & High density & 0.89 & 0.92 & \textbf{0.90} \\ 
MTCNN-Faces & Random & 0.94 & 0.62 & 0.75 \\ 
OpenPose-Faces & High density & 0.78 & 0.93 & 0.84 \\ 
OpenPose-Faces & Random & 0.72 & 0.80 & \textbf{0.76} \\ 
ViolaJones-Faces & High density & 0.96 & 0.44 & 0.60 \\ 
ViolaJones-Faces & Random & 0.44 & 0.38 & 0.41 \\ 
OpenPose-Wrists & High density & 0.66 & 1.00 & 0.79 \\ 
OpenPose-Wrists & Random & 0.88 & 0.29 & 0.43 \\ 
\hline
\end{tabular}
\caption{Detector performance on both high density samples (where proportion of targets detected was high) and random samples (where frames were randomly selected). P, R, and F denote precision, recall, and F-score, respectively. Scores in bold are the highest F-scores for each sample type.} 
\end{table}

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
  \textbf{Faces} \\
Intercept & -5.78 & 0.33 & -17.55 & 0.000 \\ 
  Close & 2.09 & 0.31 & 6.70 & 0.000 \\ 
  Far & 2.58 & 0.34 & 7.54 & 0.000 \\ 
  Prone & -0.18 & 0.08 & -2.39 & 0.017 \\ 
  Sit & 1.00 & 0.07 & 13.54 & 0.000 \\ 
  Stand & 1.50 & 0.08 & 19.98 & 0.000 \\ 
  Age & 0.17 & 0.17 & 0.97 & 0.334 \\ 
  \hline
  \textbf{Hands} \\
  Intercept & -4.84 & 0.19 & -25.40 & 0.000 \\ 
  Close & 0.88 & 0.17 & 5.25 & 0.000 \\ 
  Far & 1.77 & 0.27 & 6.45 & 0.000 \\ 
  Prone & 0.58 & 0.10 & 5.73 & 0.000 \\ 
  Sit & 1.18 & 0.10 & 12.04 & 0.000 \\ 
  Stand & 1.01 & 0.10 & 10.22 & 0.000 \\ 
  Age & 0.14 & 0.10 & 1.40 & 0.161 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from generalized linear models predicting the proportion of faces (upper panel) and wrists (lower panel) seen by children.} 
\end{table}

@@

Thanks to Kaia Simmons, Kathy Woo, and Aditi Maliwal for help in recruitment, data collection, and annotation. An earlier version of this work was presented to the Cognitive Science Society in @frank2013.

>>>>

keywords: "social cognition; face-perception; infancy; locomotion; head-cameras; deep learning"
output: cogsci2016::cogsci_paper

---
\newcommand{\wrapmf}[1]{#1}
\vspace{-1em}
```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)
```

```{r, libraries}
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(xtable)
library(lubridate)
library(langcog)
library(ggplot2)
library(ggthemes)
library(egg) # plot arranging
library(lme4)
library(gridExtra)
library(feather)
library(assertthat)

```
# Introduction
From early infancy, children are deeply engaged in learning from others [@csibra2009natural; @meltzoff2007like]. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and young infants follow overt gaze shifts [@gredeback2010]. Further, when infants attend to video stimuli, they tend to look mostly at faces at the expense of other visual information -- though older infants start to look towards people's hands and the actions they are performing [@frank2012measuring; @frank2014visual].

@@

Recent technological developments allow for testing of this hypothesis by documenting the experiences of infants and children from their own perspective. By using head-mounted cameras, researchers have begun to record the visual experiences of infants and children -- which even for walking children are extremely different from the adult perspective (and not easily predicted by our own adult intuitions) [@clerkin2017;@franchak2011;@yoshida2008]. Children’s views tend to be more restricted and dominated by objects and hands  [@yoshida2008], and computational and empirical work suggest that this restricted viewpoint may be more effective for learning objects and their labels than the comparable adult perspective [@bambach2017;@yurovsky2013statistical]. This perspective changes over the first two years of life, as views transition from primarily containing close up views of faces to capturing views of hands paired with the objects they are acting on [@fausey2016]. These changes may be driven by – or independent from – the concurrent motoric changes described above.

@@

# Function to evaluate detectors
evaluate <- function(a, b) {
  if (a == TRUE) {
    if (a == b) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (a == b) return("TN") # was not face/wrist, detected face/wrist
    else return("FP") # was not face/wrist, said face/wrist
  }
}
```

```{r  include=FALSE, echo=FALSE}
## Evalute face and wrist detectors
performanceFaces <- ground_truth_faces  %>%
  mutate(frame=as.numeric(frame), subid=video) %>%
  left_join(dlong)   %>%
  filter(detectorType!="OpenPose-Wrists") %>%
  mutate(detector_is_face = detection, is_face = as.logical(is_face)) %>%
  rowwise() %>%
  mutate(result = evaluate(is_face, detector_is_face))

@@

\begin{table}[ht]
\centering
\begin{tabular}{rllrrr}
\hline
Algorithm & Sample\ Type & P & R & F \\ 
\hline
MTCNN-Faces & High density & 0.89 & 0.92 & \textbf{0.90} \\ 
MTCNN-Faces & Random & 0.94 & 0.62 & 0.75 \\ 
OpenPose-Faces & High density & 0.78 & 0.93 & 0.84 \\ 
OpenPose-Faces & Random & 0.72 & 0.80 & \textbf{0.76} \\ 
ViolaJones-Faces & High density & 0.96 & 0.44 & 0.60 \\ 
ViolaJones-Faces & Random & 0.44 & 0.38 & 0.41 \\ 
OpenPose-Wrists & High density & 0.66 & 1.00 & 0.79 \\ 
OpenPose-Wrists & Random & 0.88 & 0.29 & 0.43 \\ 
\hline
\end{tabular}
\caption{Detector performance on both high density samples (where proportion of targets detected was high) and random samples (where frames were randomly selected). P, R, and F denote precision, recall, and F-score, respectively. Scores in bold are the highest F-scores for each sample type.} 
\vspace{-1em}
\end{table}

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
  \textbf{Faces} \\
Intercept & -5.78 & 0.33 & -17.55 & 0.000 \\ 
  Close & 2.09 & 0.31 & 6.70 & 0.000 \\ 
  Far & 2.58 & 0.34 & 7.54 & 0.000 \\ 
  Prone & -0.18 & 0.08 & -2.39 & 0.017 \\ 
  Sit & 1.00 & 0.07 & 13.54 & 0.000 \\ 
  Stand & 1.50 & 0.08 & 19.98 & 0.000 \\ 
  Age & 0.17 & 0.17 & 0.97 & 0.334 \\ 
  \hline
  \textbf{Hands} \\
  Intercept & -4.84 & 0.19 & -25.40 & 0.000 \\ 
  Close & 0.88 & 0.17 & 5.25 & 0.000 \\ 
  Far & 1.77 & 0.27 & 6.45 & 0.000 \\ 
  Prone & 0.58 & 0.10 & 5.73 & 0.000 \\ 
  Sit & 1.18 & 0.10 & 12.04 & 0.000 \\ 
  Stand & 1.01 & 0.10 & 10.22 & 0.000 \\ 
  Age & 0.14 & 0.10 & 1.40 & 0.161 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from generalized linear models predicting the proportion of faces (upper panel) and wrists (lower panel) seen by children.} 
\vspace{-1em}
\end{table}

@@

Thanks to Kaia Simmons, Kathy Woo, and Aditi Maliwal for help in recruitment, data collection, and annotation. This work was funded by a Jacobs Foundation Fellowship and a John Merck Scholars award to MCF. An earlier version of this work was presented to the Cognitive Science Society in @frank2013.

\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/amsan7/xs-face}}} \vspace{1em}
